Making Sequential Programs Deterministic

### 2019-04-06 randoop-case-study.tex

\item[\bugClasspath]
Randoop used the CLASSPATH environment variable in preference to the
classpath passed on the command line.
This can cause to incorrect behavior, both in Randoop's test suite and in the field,
if a user sets the environment variable.
The developers fixed the problem by changing Randoop to not read the environment variable
(commit 330e3c56, shown in \cref{fig:randoop-bug-getenv}).
\TheDeterminismChecker verified that all other uses of system and Java
properties did not lead to nondeterministic behavior.
\end{description}

@@

The number of \<@Det> annotations --- one per 22 lines of code --- is much
higher than we would prefer.
Nonetheless, it compares favorably to the
extensive effort by the Randoop developers (\cref{sec:subject-program}),
especially given that that \theDeterminismChecker found issues that the
developers did not.
As another point of comparison,
there are fewer type qualifiers than Java generic type arguments.

>>>>

\item[\bugClasspath]
Randoop used the CLASSPATH environment variable in preference to the
classpath passed on the command line.
This can cause incorrect behavior, both in Randoop's test suite and in the field,
if a user sets the environment variable.
The developers fixed the problem by changing Randoop to not read the environment variable
(commit 330e3c56, shown in \cref{fig:randoop-bug-getenv}).
\TheDeterminismChecker verified that all other uses of system and Java
properties did not lead to nondeterministic behavior.
\end{description}

@@

The number of \<@Det> annotations --- one per 22 lines of code --- is much
higher than we would prefer.
Nonetheless, it compares favorably to the
extensive effort by the Randoop developers (\cref{sec:subject-program}),
especially given that \theDeterminismChecker found issues that the
developers did not.
As another point of comparison,
there are fewer type qualifiers than Java generic type arguments.
